Group Fou\\*R* Term Project

### 2018-12-16 Draft.Rmd
.

---
title: "Group Fou\\*R* Term Project"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
date: "December 2018"
output: html_document
---
## Explanatory Data Analysis of Trade Statistics of Turkey

### Abstract

We worked on trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) both for export and import.Our aim is to analyze Turkey?s trade characteristics by product groups. Within this aim, we take trade values and quantities by product groups in MS Excel file format from trademap.org website for each trade partner country for the period of 2013 - 2017. 
In this study, We applied data manipulation to make it proper for analysis and explanatory data analysis with visulations and conclude with overall statistical overview of Turkey's trade.

### Explanation of Raw Data

Following the extraction from source (Trademap.org), our raw data consist of 10 countries? trade data against Turkey. This data splits to 2 with trade direction as ?Export? and ?Import?. The other dimension is stat for trade, one is ?Quantity? of Export/Import, the other is ?Value? in thousand USD of Export/Import. Therefore we have four main data frame for each country (total of 40 excel files).

@@

### Data Preparation, Cleaning and Manipulation

@@

### Analysis

#### Breakdown of Total Export and Import of Turkey Over Countries

@@

##### YORUM VE IMAGE EKLENECEK

#### Analysis of Year by Year Change in Trade Values

@@

mean(summarytableCanadaEx$ExpChngYoy)
median(summarytableCanadaEx$ExpChngYoy)
sd(summarytableCanadaEx$ExpChngYoy)
quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25)) - (1.5*IQR)
ustsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) + (1.5*IQR)

@@

mean(summarytableCanadaIm$ImpChngYoy)
median(summarytableCanadaIm$ImpChngYoy)
sd(summarytableCanadaIm$ImpChngYoy)
quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25)) - (1.5*IQR)
ustsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) + (1.5*IQR)

@@

mean(summarytableRussianEx$ExpChngYoy)
median(summarytableRussianEx$ExpChngYoy)
sd(summarytableRussianEx$ExpChngYoy)
quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25)) - (1.5*IQR)
ustsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) + (1.5*IQR)

@@

mean(summarytableRussianIm$ImpChngYoy)
median(summarytableRussianIm$ImpChngYoy)
sd(summarytableRussianIm$ImpChngYoy)
quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25)) - (1.5*IQR)
ustsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) + (1.5*IQR)

@@

```{r, fig.height = 8, fig.width = 16}

#install.packages("gridExtra")

library(gridExtra)

grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
grid.arrange(plotRusEx, plotRusIm,  nrow = 1)

#### Analysis of Trade Deficit by Countries and Years

@@

##### An Alternative perspective to explore effects of countries

@@

Through the shiny app, it is understood that
.70% of import value from China is coming from 8 products 
.50% is from electrical machinery, equipments and machinery, mechanical appliances for China
.%70 is from commodities and mineral fuels for import from Russia
.only commodities constitute 43% of total import of Russia
.vehicles other than railway is the top product imported from Germany
.machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles

##### IMAGE EKLENECEK

#### Correlation of Trade Deficit with FX Rate and BIST100 index

>>>>

---
title: "Group Fou\\*R* Term Project"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
date: "December 2018"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
    number_sections: false
    df_print: paged
    code_folding: hide

---
# Explanatory Data Analysis of Trade Statistics of Turkey {.tabset .tabset-fade .tabset-pills}

## Abstract

We worked on trade statistics data of Turkey against the G7 countries and 3 more countries (Russia, India, China) both for export and import.Our aim is to analyze Turkey's trade characteristics by product groups. Within this aim, we take trade values and quantities by product groups in MS Excel file format from trademap.org website for each trade partner country for the period of 2013 - 2017. 
In this study, We applied data manipulation to make it proper for analysis and explanatory data analysis with visulations and conclude with overall statistical overview of Turkey's trade.

## Explanation of Raw Data

Following the extraction from source (Trademap.org), our raw data consist of 10 countries' trade data against Turkey. This data splits to 2 with trade direction as 'Export' and 'Import'. The other dimension is stat for trade, one is 'Quantity' of Export/Import, the other is 'Value' in thousand USD of Export/Import. Therefore we have four main data frame for each country (total of 40 excel files).

@@

## Data Preparation, Cleaning and Manipulation

@@

## Analysis

### Breakdown of Total Export and Import of Turkey Over Countries

@@

#### YORUM VE IMAGE EKLENECEK

### Analysis of Year by Year Change in Trade Values

@@

#mean(summarytableCanadaEx$ExpChngYoy)
#median(summarytableCanadaEx$ExpChngYoy)
#sd(summarytableCanadaEx$ExpChngYoy)
#quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.25)) - (2*IQR)
ustsinir=quantile(summarytableCanadaEx$ExpChngYoy, probs = c(0.75)) + (2*IQR)

@@

#mean(summarytableCanadaIm$ImpChngYoy)
#median(summarytableCanadaIm$ImpChngYoy)
#sd(summarytableCanadaIm$ImpChngYoy)
#quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.25)) - (2*IQR)
ustsinir=quantile(summarytableCanadaIm$ImpChngYoy, probs = c(0.75)) + (2*IQR)

@@

#mean(summarytableRussianEx$ExpChngYoy)
#median(summarytableRussianEx$ExpChngYoy)
#sd(summarytableRussianEx$ExpChngYoy)
#quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) - quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.25)) - (2*IQR)
ustsinir=quantile(summarytableRussianEx$ExpChngYoy, probs = c(0.75)) + (2*IQR)

@@

#mean(summarytableRussianIm$ImpChngYoy)
#median(summarytableRussianIm$ImpChngYoy)
#sd(summarytableRussianIm$ImpChngYoy)
#quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25, 0.50, 0.75, 1))
IQR= quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) - quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25))
altsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.25)) - (2*IQR)
ustsinir=quantile(summarytableRussianIm$ImpChngYoy, probs = c(0.75)) + (2*IQR)

@@

```{r, echo=FALSE, fig.height=7, fig.width=10 }

plotCanEx
plotCanIm
plotRusEx
plotRusIm

#grid.arrange(plotCanEx, plotCanIm,  nrow = 1)
#grid.arrange(plotRusEx, plotRusIm,  nrow = 1)
#fig.height=8, fig.width=16
```

### Analysis of Trade Deficit by Countries and Years

@@

#### An Alternative perspective to explore effects of countries

@@

Through the shiny app, it is understood that
* 70% of import value from China is coming from 8 products 
* 50% is from electrical machinery, equipments and machinery, mechanical appliances for China
* %70 is from commodities and mineral fuels for import from Russia
* Only commodities constitute 43% of total import of Russia
* Vehicles other than railway is the top product imported from Germany
* Machinery, mechanical appliances are the second product imported from Germany and its share is so close to vehicles

#### IMAGE EKLENECEK

### Correlation of Trade Deficit with FX Rate and BIST100 index
